Super awesome embeddings

### 2019-02-03 paper/main.tex
Fill discussion for last two experiments

\section{Experiments}
\subsection{Assumptions}
Since our goal is to check how embedding approach works for WSD problem, we use pretrained embedding model from spaCy - en\_vectors\_web\_lg.
Due to high impact of training data order on test results, as a result we take average score of 30 runs for each optimization with random order of training data.
\subsection{Baseline}
First of experiments is to check how out-of-the-box model works without extra optimizations. We perform tests with different context lengths, as a score we choose top 1 and top 3 accuracy. Results are shown in the Fig. \ref{fig:baseline}.

@@

\begin{figure}
    \label{fig:exp3}
    \caption{Based on fixed context length and alpha parameter value, comparison of the alpha-optimized model and a alpha-optimized model with various beta parameters. }
    \includegraphics[scale=0.5]{res/exp3_beta_top_acc.png}
\end{figure}
TODO: Some discussion.

\subsection{Longer training}
Previous optimization are applied for only one epoch of training. The goal of next experiment is to check how number of epochs affects final accuracy. We run up to 5 epochs of training using parameters obtained in previous experiments. Results are shown in the Fig. \ref{fig:exp4_2}.
\begin{figure}
    \label{fig:exp4_1}
    \caption{5 epoch training of optimized model}
    \includegraphics[scale=0.6]{res/exp4_epoch_top_acc.png}
\end{figure}
We see that there is almost no improvement after first epoch of training. Probably the problem is that alpha and beta parameters are too big. We also check what happens when we choose lower values of alpha/beta parameters. Results are shown in the Fig. \ref{fig:exp4_2}.
\begin{figure}
    \label{fig:exp4_2}
    \caption{Comparison of multiple optimized models across 5 epochs of training. }
    \includegraphics[scale=0.6]{res/exp4_epoch_multiconfiguration_top_acc.png}
\end{figure}
TODO: Some discussion.

>>>>

\section{Experiments}
\subsection{Assumptions}
Since our goal is to check how embedding approach works for WSD problem, we use pretrained embedding model from spaCy - en\_vectors\_web\_lg.
Due to high impact of training data order on test results, as a result we take average score of 30 runs for each optimization with random order of training data. The best configuration of each experiment is taken as a baseline for the next experiment.
The goal of these experiments is to show how each of parameters influences on model's accuracy after training.
\subsection{Baseline}
First of experiments is to check how out-of-the-box model works without extra optimizations. We perform tests with different context lengths, as a score we choose top 1 and top 3 accuracy. Results are shown in the Fig. \ref{fig:baseline}.

@@

\begin{figure}
    \label{fig:exp3}
    \caption{Based on fixed context length and alpha parameter value, comparison of the alpha-optimized model and a alpha-optimized model with various beta parameters. }
    \includegraphics[scale=0.5]{res/exp3_beta_top_acc.png}
\end{figure}
Beta parameter is also a scalar value and it is responsible for increasing distance between keyword and incorrect context (Equation \ref{eq:beta_optimization}) . In the graph of results we see that for low value of beta there is an improvement in top 1 accuracy, for top 3 accuracy the score goes under baseline value. It is interesting as we improve top 1 score and worsen top 3 score. Probably beta parameter should not be optimized during single epoch training and should be very slow as increasing distances between two incorrect embeddings may cause that we also increase distance between correct pair of embeddings.

\subsection{Longer training}
Previous optimization are applied for only one epoch of training. The goal of this experiment is to check how number of epochs affects final accuracy. We run up to 5 epochs of training using parameters obtained in previous experiments. Results are shown in the Fig. \ref{fig:exp4_2}.
\begin{figure}
    \label{fig:exp4_1}
    \caption{5 epoch training of optimized model}
    \includegraphics[scale=0.6]{res/exp4_epoch_top_acc.png}
\end{figure}
We see that there is almost no improvement after first epoch of training. Probably the problem is that alpha and beta parameters are too big. We also check what happens when we choose lower values of alpha/beta parameters. Results are shown in the Fig. \ref{fig:exp4_2}.
\begin{figure}
    \label{fig:exp4_2}
    \caption{Comparison of multiple optimized models across 5 epochs of training. }
    \includegraphics[scale=0.6]{res/exp4_epoch_multiconfiguration_top_acc.png}
\end{figure}
Longer training shows that optimal parameters obtained from previous experiments are not good for longer training and lower values of alpha and beta parameters are better. Probably we should use additional decays parameters to decrease values of alpha and beta parameters.
